---
title: "Data Products Final Project"
author: "Christian Suarez"
date: "24/4/2020"
output: ioslides_presentation
---


```{r setup, include=TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Application

This application has been developed to allow analyze behavor of automovilistic accidents in Medellin Colombia and It contains information from from 2014 to 2017.

The application has been built using shiny in the following URL:
https://christian-suarez-gil.shinyapps.io/DataProductsProject/


## Source code

The source code can be found here:
https://github.com/christiancalidad/DataProductsProject


```{r, echo=FALSE,message=FALSE,error=FALSE}

```

## Guide

Trough this application you can analyze behavor of automovilistic accidents in Medellín City - Colombia,

To use it, please follow the next steps:

- Select the date range from January 2014 to December 2017.

- Select the time scale you want to visualice

- Click on Refresh Button


```{r, echo=FALSE,message=FALSE,error=FALSE}

```


## Running

When you select weekly or monthly scale, the application summarize the daily data trough the following expression:
```{r, include=FALSE,message=FALSE,error=FALSE}
setwd("C:/Users/CHRISTIAN/Desktop/Coursera/Specialization/2/DataProducts/FinalProject/Presentation")
DatosDia <- read.delim("Base_Diaria.csv", header=TRUE, sep=",", encoding = "UTF-8")
DatosDia$Fecha<-as.Date(DatosDia$Fecha,"%Y-%m-%d")
SerieDia <- aggregate(Accidentes~Fecha*CLASE,data=DatosDia,FUN=sum)
Base <- SerieDia
```

```{r, echo=TRUE,message=FALSE,error=FALSE,eval=TRUE}
SerieGraph <- aggregate(Accidentes~Fecha*CLASE,data=Base,FUN=sum)
SerieGraph$Fecha <-format(SerieGraph$Fecha,"%G-%V")
SerieGraph <- aggregate(Accidentes~Fecha*CLASE,data=SerieGraph,FUN=sum)
head(SerieGraph)
```

